Respiratory-Related Mortality Rates Show A Positive Correlation With Increasing Air Pollution

### 2024-03-16 paper/paper.qmd
Final paper

---
title: "Respiratory-Related Mortality Rates Show A Positive Correlation With Increasing Air pollution"
subtitle: "Based on Data Collected From The Province Of Alberta"
author: 
  - Vanshika Vanshika
  - Shivank Goel
  - Navya Hooda
thanks: "Code and data are available at: https://github.com/shivankgoel003/Mortality-in-Alberta."
date: today
date-format: long
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
format: pdf
number-sections: true
bibliography: references.bib
---

>>>>

---
title: "Respiratory-Related Mortality Rates Show A Positive Correlation With Increasing Air Pollution"
subtitle: "Based on Data Collected From The Province Of Alberta"
author: 
  - Vanshika Vanshika
  - Shivank Goel
  - Navya Hooda
thanks: "Code and data are available at: https://github.com/shivankgoel003/Mortality-in-Alberta."
date: today
date-format: long
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
format: pdf
number-sections: true
bibliography: references.bib
---
